### 2017-10-22 paper/sections/1_introduction.tex
paper: figure 1 replace client with semantics
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What did we do
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a setup in
our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art HPC
architectures.  The HDFS\footnote{This is example is not directly evaluated in
this paper, although a similar use case is explored in~\S\ref{use-case-1}}
subtree has weaker consistency than strong consistency because it  does not
guarantee that all updates are not immediately seen by all servers; the BatchFS
and RAMDisk subtrees are decoupled from the global namespace and have similar
consistency/durability behavior to those systems; and the POSIX subtree retains
the rigidity of POSIX's strong consistency.

@@

% Results
Our results confirm the assertions of ``clean-state" research systems that
decouple namespaces; specifically that the technique drastically improves
performance (104\(\times\) speed up) but we go a step further by quantifying
the costs of merging updates (7\(\times\) slow down) and maintaining durability
(\(10\times\) slow down). We also show the effect of having a metadata specific
file format in systems that are based on in-memory data structures.  We scale
up to 20 clients executing an extremely metadata intensive job because this
workload exhausts the resources of a single metadata server for the code base we
built on.  Partitioning and replicating metadata across a cluster can be
controlled with something like Mantle~\cite{sevilla:sc15-mantle}, but in this
paper we show the capacity and performance of a metadata server with superior
metadata protocols, which should be used to inform load balancing decisions.

>>>>

% What did we do
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a setup in
our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art HPC
architectures.  The HDFS\footnote{HDFS itself is not directly evaluated in this
paper, although the HDFS semantics and their performance is explored
in~\S\ref{sec:use-case-1}} subtree has weaker consistency than strong
consistency because it  does not guarantee that all updates are not immediately
seen by all servers; the BatchFS and RAMDisk subtrees are decoupled from the
global namespace and have similar consistency/durability behavior to those
systems; and the POSIX subtree retains the rigidity of POSIX's strong
consistency.

@@

% Results
Our results confirm the assertions of ``clean-state" research systems that
decouple namespaces; specifically that the technique drastically improves
performance (104\(\times\) speed up) but we go a step further by quantifying
the costs of merging updates (7\(\times\) slow down) and maintaining durability
(\(10\times\) slow down). We also show the effect of having a metadata specific
file format in systems that are based on in-memory data structures.  Our
prototype is built on Ceph because it was originally designed for HPC and has
proven to be useful for HPC workloads~\cite{}. Several features were motivated
by HPC requirements~\cite{weil:osdi2006-ceph}, so the lessons are useful (and
can be implemented) in HPC environments.

### 2017-10-22 paper/sections/3_posix_overheads.tex
paper: figure 1 replace client with semantics
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% CITEME PDSW paper
In our examination of the overheads of POSIX we benchmark and analyze CephFS,
the file system that uses Ceph's object store ({\it i.e.} RADOS) to store its
data and metadata. Ceph was originally designed for HPC and has proven to be
useful for HPC workloads~\cite{}. Several features were motivated by HPC
requirements~\cite{weil:osdi2006-ceph}, so the lessons are useful (and can be
implemented) in HPC environments.  This file system is an implementation of one
set of design decisions and our goal is to highlight the effect that those
decisions have on performance. During this process we discovered, based on the
analysis and breakdown of costs, that durability and consistency have high
overhead.

To show how the file system behaves under high metadata load we use a
create-heavy workload. Create-heavy workloads are studied the most in HPC
research because of the checkpoint/restart use case but they also happen to
stress the underlying storage system the most.
Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The \texttt{untar} phase, which is characterized by many creates, has
the highest resource usage which suggests that it is stressing the consistency
and journaling subsystems of the metadata server the most. Traditional file
system techniques for improving performance, such as caching inodes, do not
help for create-heavy workloads.

>>>>

% CITEME PDSW paper
In our examination of the overheads of POSIX we benchmark and analyze CephFS,
the file system that uses Ceph's object store ({\it i.e.} RADOS) to store its
data and metadata. To show how the file system behaves under high metadata load
we use a create-heavy workload. Create-heavy workloads are studied the most in
HPC research because of the checkpoint/restart use case but they also happen to
stress the underlying storage system the most.  During this process we
discovered, based on the analysis and breakdown of costs, that durability and
consistency have high overhead but we urge the read to keep in mind that this
file system is an implementation of one set of design decisions and our goal
here is to highlight the effect that those decisions have on performance.

Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The \texttt{untar} phase, which is characterized by many
creates, has the highest resource usage which suggests that it is stressing the
consistency and journaling subsystems of the metadata server the most.
Traditional file system techniques for improving performance, such as caching
inodes, do not help for create-heavy workloads.

### 2017-10-22 paper/sections/6_results.tex
paper: figure 1 replace client with semantics
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

>>>>

We scale
up to 20 clients executing an extremely metadata intensive job because this
workload exhausts the resources of a single metadata server for the code base we
built on.  Partitioning and replicating metadata across a cluster can be
controlled with something like Mantle~\cite{sevilla:sc15-mantle}, but in this
paper we show the capacity and performance of a metadata server with superior
metadata protocols, which should be used to inform load balancing decisions.
